Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-23 introduction.tex
Fixes and more contribution description

In this work we present PS, a multiobjective design exploration
strategy that introduces the concept of Parameter Space Representation
of Pareto Set. The main idea is focusing on the ``innovation''
introduced in the Pareto sets and then accordingly distributing the
exploration effort in regions created in the multidimensional space of
system parameters. \comment{Potrebbe essere pompato di piu' con qualche cosa piu' d'impatto? }

>>>>

In this work we present a multiobjective design exploration strategy
that introduces the concept of Parameter Space Representation of
Pareto Set (PS). The main idea is focusing on the ``innovation''
introduced in the Pareto sets and then accordingly distributing the
exploration effort in regions created in the multidimensional space of
system parameters. The aim of the PS approach is to propose a new
perspective on the configuration space, where parameter
interdependencies play the fundamental role of making some regions
more capable of generating hardly predictable solutions: catching this
sort of ``chaoticity'' in the parameter space is the main idea behind
the strategy that is being introduced in this work.

\comment{Potrebbe essere pompato di piu' con qualche cosa piu' d'impatto? }
